Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-30 paper/paper_new.tex
Updates from Overleaf

\section{Introduction}
\begin{figure}[H]
  \centering
  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
  \hspace{4mm}
  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \label{fig:teaser}
\end{figure}
Over the last several decades advances in computing, imagine, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens. Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-is millions appropriate?} of biological specimens. These digital specimen images globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
%{jane} not sure this note is mine? should we integrate machine learning into intro. As researchers seek to apply computational methods, and explore AI, significant challenges surface..)

>>>>

\section{Introduction}
\begin{figure}[H]
  \centering
  \includegraphics[width=.45\textwidth]{images/teaser1_crop}
  \hspace{4mm}
  \includegraphics[width=.45\textwidth]{images/teaser2_crop}
  \caption{Initial object detection on specimen images using Detectron2~\cite{wu2019detectron2}}
  \label{fig:teaser}
\end{figure}
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have digital specimens. Additionally, initiatives, such as National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program, which ran for nearly a decade, have supported the digitization and curation of millions \todo{Hank-millions?} of biological specimens. These digital specimen images are globally available through a range of open access repositories; they enable researchers, educators, students, and the general public to examine and compare in ways previously unimaginable. Significant challenges surface, however, when researchers seek to apply computational methods to these data items, due to both image quality and metadata issues.
%{jane} not sure this following mine: "As researchers seek to apply computational methods, and explore AI, significant challenges surface..)" 
%should we try to insert machine learning here?
